\documentclass{ExpressiveCoverLetter}

\begin{document}

\coverletterheader[
    % firstname=Ram,
    middleinitial=Ram Polisetti,
    % lastname=Polisetti,
    email=rampolisettius@gmail.com,
    phone=716-256-7258,
    linkedin=ram-polisetti,
    % github=ram-polisetti,
    % city=Seattle,
    state=WA
]

\vspace{0.25in}
\today
\vspace{0.15in}


I am excited to apply for the Data Engineer position at Infosys. With a
strong background in data engineering and a passion for designing and
building large-scale data systems, I am confident that I would be a
great fit for this role.

As a data engineer with 3 years of experience, I have developed a strong
expertise in data pipeline development, data processing, and data
storage solutions. I have worked with a range of technologies, including
Apache Spark, Hadoop, NoSQL databases, and cloud computing platforms. My
experience in database development, Big Data development, and ETL
activities has equipped me with the skills to design and implement
efficient data flow pipelines and prepare databases for visualization
and analytics.

I am particularly drawn to this role at Infosys because of the
opportunity to work on analytics projects and paid POVs for Infosys BPO
analytics. I am excited about the prospect of working with a talented
team to drive business growth and improvement through data-driven
insights.

In addition to my technical skills, I possess excellent communication
and analytics skills, which have been essential in my previous roles. I
am a team player and have a proven ability to work effectively in
fast-paced environments.

Thank you for considering my application. I would be thrilled to discuss
this opportunity further and explain in greater detail why I am the
ideal candidate for this role.

Sincerely,

\vspace{.15in}

Ram Polisetti

\end{document}