\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    % firstname=Sai Teja,
    middleinitial=Ram Polisetti,
    % lastname=Ram Polisetti,
    email=rampolisettius@gmail.com,
    phone=716-256-7258,
    linkedin=ram-polisetti,
    github=ram-polisetti,
    city=Seattle,
    fixobjectivespacing=true
]

\objective{Dynamic and results-driven Operations Manager with over 2 years of experience in software engineering, web/mobile application development, and agile methodologies.}

% ----- Education -----
\section{Education}

\experience{Master of Science}{Data Science}{Sept 2022}{Jan 2024}{
    \noindent School of Engineeng and Applied Sciences \newline
    State University of New York (UB), Buffalo, NY
}

% ------ Skills -----
\section{Skills}
\skills{Python, R, SQL, Tableau, Amazon Redshift, Amazon Quicksight,
    Machine Learning, Data Analysis \& Visualization, Operations Management,
    Inventory Management, Supply Chain Optimization, Logistics Management,
    KPI Tracking, Root Cause Analysis, Team Leadership
}

% ----- Work Experience -----
\section{Work Experience}

\experience{JerseyStem, New Jersey}{Data Analyst}{Mar 2024}{Present}{
    \achievement{Spearheaded the creation of advanced automated data pipelines using \tech{SQL}, \tech{Python}, and \tech{Alteryx}, significantly enhancing data collection and analysis to inform decision-making and improve program effectiveness.}
    \achievement{Orchestrated \tech{Postman} and \tech{Webhooks} for real-time data integration and automation, optimizing data workflows and ensuring organizational agility and responsiveness to evolving data trends and needs.}
    \achievement{Launched a daily reporting system using \tech{AppSheet}, \tech{Tableau}, and \tech{Google Data Studio}, providing actionable insights and enhancing organizational accountability and project deliverables through superior data visualization.}

}

\experience{Amazon Inc., Hyderabad, India}{Transportation Specialist}{Nov 2020}{Jul 2022}{
    \achievement{Executed data-driven optimizations of dispatch systems using advanced \tech{SQL} queries to extract data from \tech{Amazon Redshift}, resulting in a 40\% increase in efficiency and a 15\% decrease in carrier-related fraud.}
    \achievement{Led a data analysis project to strategically reduce equipment dwell times, reintegrating over 1,000 equipment and improving logistics and supply chain efficiency.}
    \achievement{Spearheaded comprehensive transportation data analysis to enhance route efficiency, cutting down empty miles by 8\% and reducing logistical costs through \tech{SQL} and data visualization tools.}
    \achievement{Monitored and analyzed logistics performance metrics using \tech{Amazon Quicksight}, achieving a 20\% reduction in operational incidents and improving delivery timelines.}
    \achievement{Developed Standard Operating Procedures (SOPs) and automated transportation operations, leading to a 30\% reduction in team acclimatization time and improvements in overall team efficiency.}
    \achievement{Directed and mentored a team of 5 at Amazon, earning recognition as a Subject Matter Expert in logistics data analysis and receiving the "Amazon Leadership Principle Award" for initiative in dispatch systems.}

}

% ----- Technical Projects -----

\section{Technical Projects}

\project{SQL, Python, Tableau, Redshift, Quicksight}{Advanced Supply Chain Freight Analytics Dashboard}{}{}{
    \achievement{Developed a dashboard providing real-time insights into transportation and supply chain operations, using \tech{SQL}, \tech{Python}, and \tech{Tableau}.}
    \achievement{Conducted in-depth transportation data analysis, identifying key trends and patterns to optimize route efficiency and carrier performance.}
    \achievement{Established and monitored KPIs to measure transportation performance, contributing to improvement in delivery times and cost savings.}
    \achievement{Performed root cause analysis to address transportation inefficiencies, leading to a 15\% reduction in logistical bottlenecks.}
    \achievement{Effectively communicated complex data insights to stakeholders through regular reports and presentations, enhancing decision-making processes.}
}

\project{Python, Plotly, SQL, Monte Carlo Simulation}{Strategic Route Optimization and Cost Minimization}{}{}{
    \achievement{Engineered a network optimization strategy using \tech{NetworkX}, delineating 30 critical plant-port connections, thereby enhancing logistical efficiency and reducing route costs.}
    \achievement{Created a constraint-based allocation model for 50+ products and 30 customers, achieving a 100\% adherence to Vendor Managed Inventory (VMI) protocols and minimizing supply discrepancies.}
    \achievement{Improved decision-making processes by developing interactive dashboards with \tech{Plotly}, providing stakeholders with clear insights for strategic supply chain decision-making.}
}

% \project{Python, SQL, KPI Identification}{Supply Chain Optimization through Data Analytics}{}{}{
%     \achievement{Led analysis of supply chain data, extracting key metrics to refine inventory management and inform data-centric marketing strategies.}
%     \achievement{Analyzed supplier performance to address inefficiencies, implementing solutions that bolstered supply chain resilience and led to a measurable decrease in defect rates.}
%     \achievement{Employed sophisticated data visualization methodologies to uncover and act upon trends within customer demographics and pricing strategies, driving improvements in logistical operations, and influencing cost-saving measures.}
% }



\end{document}