\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    % firstname=Sai Teja,
    middleinitial=Ram Polisetti,
    % lastname=Ram Polisetti,
    email=rampolisettius@gmail.com,
    phone=716-256-7258,
    linkedin=ram-polisetti,
    github=ram-polisetti,
    city=Seattle,
    fixobjectivespacing=true
]

\objective{Dynamic and results-driven Operations Manager with over 2 years of experience in software engineering, web/mobile application development, and agile methodologies.}

% ----- Education -----
\section{Education}

\experience{Master of Science}{Data Science}{Sept 2022}{Jan 2024}{
    \noindent State University of New York (UB), Buffalo, NY
}

% ------ Skills -----
\section{Skills}
\skills{
    Machine Learning, Deep Learning, Natural Language Processing,
    Predictive Modeling, Data Mining, Statistical Analysis, Data
    Visualization, Python, R, SQL, TensorFlow, PyTorch, Scikit-learn,
    Keras, Tableau, Power BI, AWS, Azure, Big Data, Hadoop, Spark,
    Data Wrangling, Data Preprocessing, Feature Engineering, Model
    Evaluation, Model Deployment
}

% ----- Work Experience -----
\section{Work Experience}

\experience{JerseyStem, New Jersey}{Data Analyst}{Mar 2024}{Present}{
    \achievement{Spearheaded the optimization of data processing workflows, resulting in a 25\% reduction in data processing time and a 15\% increase in data quality, saving the company \$30,000 annually.}
    \achievement{Facilitated the development of data visualizations to communicate insights to stakeholders, achieving a 90\% adoption rate among business users and a 20\% increase in data-driven decision-making, leading to a 12\% increase in sales revenue.}
}

\experience{Amazon Inc., Hyderabad, India}{Transportation Specialist}{Nov 2020}{Jul 2022}{
    \achievement{Streamlined transportation operations by identifying and eliminating inefficiencies, resulting in a 15\% reduction in transportation costs and a 10\% increase in on-time delivery rates, saving the company \$150,000 annually.}
    \achievement{Collaborated with transportation teams to design and implement process improvements, achieving a 20\% reduction in transit times and a 15\% increase in route optimization, leading to a 10\% reduction in fuel consumption.}
    \achievement{Negotiated with transportation providers to secure better rates and service levels, resulting in a 12\% reduction in costs and a 10\% increase in capacity utilization, saving the company \$100,000 annually.}
    \achievement{Orchestrated the implementation of transportation management systems and tools, achieving a 25\% reduction in manual errors and a 15\% increase in productivity, leading to a 10\% reduction in operational costs.}
}

\experience{National Instruments}{Analyst Intern}{Nov 2018}{Feb 2020}{
    \achievement{Built and deployed predictive models using statistical and machine learning techniques, achieving a 90\% accuracy rate in forecasting product demand and a 15\% reduction in inventory costs, saving the company \$50,000 annually.}
    \achievement{Investigated manufacturing data to identify opportunities for process improvements and cost savings, resulting in a 10\% reduction in production costs and a 5\% increase in product quality, leading to a 5\% increase in sales revenue.}
    \achievement{Enhanced dashboards and reports to track key performance indicators (KPIs) and metrics, achieving a 95\% completion rate for reports and a 10\% increase in data-driven decision-making, leading to a 5\% increase in sales revenue.}
}

% ----- Technical Projects -----

\section{Technical Projects}

\project{SQL, Python, Tableau, Redshift, Quicksight}{Advanced Supply Chain Freight Analytics Dashboard}{}{}{
    \achievement{Developed a dashboard providing real-time insights into transportation and supply chain operations, using \tech{SQL}, \tech{Python}, and \tech{Tableau}.}
    \achievement{Conducted in-depth transportation data analysis, identifying key trends and patterns to optimize route efficiency and carrier performance.}
    \achievement{Established and monitored KPIs to measure transportation performance, contributing to improvement in delivery times and cost savings.}
    \achievement{Performed root cause analysis to address transportation inefficiencies, leading to a 15\% reduction in logistical bottlenecks.}
    \achievement{Effectively communicated complex data insights to stakeholders through regular reports and presentations, enhancing decision-making processes.}
}

\project{Python, Plotly, SQL, Monte Carlo Simulation}{Strategic Route Optimization and Cost Minimization}{}{}{
    \achievement{Engineered a network optimization strategy using \tech{NetworkX}, delineating 30 critical plant-port connections, thereby enhancing logistical efficiency and reducing route costs.}
    \achievement{Created a constraint-based allocation model for 50+ products and 30 customers, achieving a 100\% adherence to Vendor Managed Inventory (VMI) protocols and minimizing supply discrepancies.}
    \achievement{Improved decision-making processes by developing interactive dashboards with \tech{Plotly}, providing stakeholders with clear insights for strategic supply chain decision-making.}
}

% \project{Python, SQL, KPI Identification}{Supply Chain Optimization through Data Analytics}{}{}{
%     \achievement{Led analysis of supply chain data, extracting key metrics to refine inventory management and inform data-centric marketing strategies.}
%     \achievement{Analyzed supplier performance to address inefficiencies, implementing solutions that bolstered supply chain resilience and led to a measurable decrease in defect rates.}
%     \achievement{Employed sophisticated data visualization methodologies to uncover and act upon trends within customer demographics and pricing strategies, driving improvements in logistical operations, and influencing cost-saving measures.}
% }



\end{document}